Manuscript figures

### 2025-12-14 manuscriptFigures.Rmd
added et plot to burn v unburn, updating filepaths

nse <- read_csv('./38HRU_oct2025_updates/nseCats.csv') %>%
  filter(year == c('All')) %>%
  dplyr::select(input_data, year_missing, nse)
perf <- left_join(nse, pbias, by = c('input_data',
                                     'year_missing'))

# assign categories
perf <- perf %>%
  mutate(performance = case_when(
                                nse < 0.5 & abs(pbias) >= 25 ~ 'Neither',
                                nse > 0.5 & abs(pbias) >= 25 ~ 'NSE',
                                nse < 0.5 & abs(pbias) < 25 ~ '% bias satisfactory',
                                nse > 0.5 & abs(pbias) < 25 ~ 'NSE + % bias satisfactory')) %>%
  mutate(input_data = if_else(input_data == 'grid',
                              'Gridded', 'Station'),
         year_missing = if_else(year_missing == 'None',
                                'all', year_missing))
perf1 <- perf %>%
  mutate(year_missing = if_else(year_missing == 'all',
                                'none',
                                year_missing))

@@

unburn <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_2_unburn.csv') %>%
  mutate(date = mdy(time),
         year = year(date),
         type = 'unburn') %>%
  filter(year == 2016)

burn <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_5_burn.csv') %>%
  mutate(date = mdy(time),
         year = year(date),
         type = 'burn') %>%
  filter(year == 2016)

@@

@@

@@

p_plot <- p_plot + theme(legend.position = "none")
int_plot <- int_plot + theme(legend.position = "none")
soilsat_plot <- soilsat_plot + theme(legend.position = "none")
interflow_plot <- interflow_plot + theme(legend.position = "none")
gw_plot <- gw_plot + theme(legend.position = "none")
swe_plot <- swe_plot + theme(legend.position = "none")

plots <- plot_grid(p_plot,
          int_plot,
          swe_plot,
          soilsat_plot,
          interflow_plot,
          gw_plot,
          ncol = 3)

@@

ggsave('./figures/figure10.png',
       dpi=800,
       bg='white',
       height=8,
       width=12)

@@

perf <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/perf_metrics.csv')

@@

pbias_kge <- ggplot(perf1, aes(x=KGE, y=pbias, color=type)) + 
  #geom_point(size=4, alpha=0.8) +
  geom_jitter(size = 4, alpha = 0.7, width = 0.001, height = 0.001) +
  theme_bw(base_size=20) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y = '% bias') +
  theme(
    legend.position = 'bottom',
    legend.text = element_text(size = 16),
    legend.title = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    panel.grid.major.x = element_blank()  # remove vertical major grid lines
   # panel.grid.minor.x = element_blank(),
    #panel.grid.minor = element_blank()      # remove all minor grid lines

@@

# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_nse_pbias.png',
#        dpi=600,
#        width=10,
#        height=6)

>>>>

# assign categories
perf <- perf %>%
  mutate(performance = case_when(
                                nse < 0.5 & abs(pbias) >= 25 ~ 'Neither',
                                nse > 0.5 & abs(pbias) >= 25 ~ 'NSE',
                                nse < 0.5 & abs(pbias) < 25 ~ '% bias satisfactory',
                                nse > 0.5 & abs(pbias) < 25 ~ 'NSE + % bias satisfactory')) %>%
  mutate(input_data = if_else(source == 'grid',
                              'Gridded', 'Station'),
         year_missing = if_else(year_missing == 'None',
                                'all', year_missing))
perf1 <- perf %>%
  mutate(year_missing = if_else(year_missing == 'all',
                                'none',
                                year_missing))

@@

unburn <- read_csv('./38HRU_oct2025_updates/HRU/statn_HRU_2_unburn.csv') %>%
  mutate(date = mdy(time),
         year = year(date),
         type = 'unburn') %>%
  filter(year == 2016)

burn <- read_csv('./38HRU_oct2025_updates/HRU/statn_HRU_5_burn.csv') %>%
  mutate(date = mdy(time),
         year = year(date),
         type = 'burn') %>%
  filter(year == 2016)

@@

et <- both %>%
  dplyr::select(date, type, actET)

@@

et_plot <- ggplot(et, aes(x = date,
                        y = actET, 
                        color = type)) +
  geom_line(size=1, alpha=0.7) +
    scale_color_manual(values = c("burn" = "red", 
                                  "unburn" = "black")) +
  scale_x_date(date_labels = "%b") +
  labs(x = element_blank(),
       y = 'ET (mm)') +
  theme_bw(base_size = 20) +
  theme(legend.position = 'bottom',
    #legend.position = c(0.24, 0.852), 
    legend.text = element_text(size = 10),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    legend.key.width = unit(1, "cm")
  )

et_plot

@@

p_plot <- p_plot + theme(legend.position = "none")
int_plot <- int_plot + theme(legend.position = "none")
soilsat_plot <- soilsat_plot + theme(legend.position = "none")
interflow_plot <- interflow_plot + theme(legend.position = "none")
gw_plot <- gw_plot + theme(legend.position = "none")
swe_plot <- swe_plot + theme(legend.position = "none")
et_plot <- et_plot + theme(legend.position = "none")

plots <- plot_grid( #p_plot,
          int_plot,
          swe_plot,
          soilsat_plot,
          et_plot,
          interflow_plot,
          gw_plot,
          ncol = 3)

@@

ggsave('./figures/figure10_oct2025.png',
       dpi=800,
       bg='white',
       height=8,
       width=12)

@@

perf <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/perf_metrics.csv')

@@

pbias_kge <- ggplot(perf1, aes(x=KGE, y=Bias, color=type)) + 
  #geom_point(size=4, alpha=0.8) +
  geom_jitter(size = 4, alpha = 0.7, width = 0.001, height = 0.001) +
  theme_bw(base_size=20) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y = 'Bias') +
  theme(
    legend.position = 'bottom',
    legend.text = element_text(size = 16),
    legend.title = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    panel.grid.major.x = element_blank()  # remove vertical major grid lines
   # panel.grid.minor.x = element_blank(),
    #panel.grid.minor = element_blank()      # remove all minor grid lines

@@

ggsave('/Users/megansears/Documents/Repos/fourmile/figures/figure11_oct2025.png',
       dpi=600,
       width=10,
       height=6)
